% Master-Thesis: Indoor self-localization with Smartphones using iBeacons
% Thomas Bopst (MSI)
% HTWG-Konstanz
%
% Date: 01.10.2014
%

\documentclass[11pt,a4paper]{report}

% Own packages
\usepackage[utf8]{inputenc}
\usepackage[german, english]{babel}
\usepackage{courier}
\usepackage[]{natbib}

\usepackage{listings}
\lstset{numbers=left, numberstyle=\tiny, numbersep=20pt} % Programmcode einfügen
\lstset{basicstyle=\normalsize\ttfamily, breaklines=true} % \footnotesize
\lstset{language=XML}

\usepackage{pgfplots}
\usepackage{subfig}
\usepackage{floatrow}
\usepackage{mathtools}

\selectlanguage{english}

\usepackage[printonlyused]{acronym}
% PDF Eigenschaften
% -----------------
\usepackage
[
	colorlinks = false,
	bookmarks = true,
	pdftitle={Master-Thesis Indoor Self-Localization with Smartphones using iBeacons},
	pdfauthor={Thomas Bopst},
	pdfsubject={Master-Thesis},
	pdfkeywords={HTWG-Konstanz, Master-Thesis, MSI},
	urlcolor=blue,
	pdfstartview=FitH
]{hyperref}

\usepackage{titlesec}
\titleformat{\chapter}[display]
{\normalfont\huge\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\Huge}
\titlespacing*{\chapter}{0pt}{-40pt}{20pt}

% HTWG-Template
\usepackage{graphicx}
\usepackage{a4wide} % HTWG a4
%\usepackage[english]{babel}

% HTWG-Template
\newcommand{\thema}{Indoor Self-Localization with Smartphones
 using iBeacons}
\newcommand{\schlagworte}{Indoor Localization, Indoor Positioning, iBeacon, Smartphone, Particle Filter, Monte Carlo Localization}
\newcommand{\zusammenfassung}{Location-based applications are nowadays taken for granted in our life, but until now the available indoor localization systems have not been able to establish themselves. At their \acs{WWDC}~2013 Apple introduced a new technology called iBeacons. This relies on small and cheap \acl{BLE} chips which enables new location awareness features \citep{apple:wwdc_2013_bruins}.

In this thesis a new indoor self-localization solution based on \acl{MCL} is proposed. A \acl{PF} is used to combine \acs{RSS} based distance estimations to deployed beacons, with the user's motion, as determined by the smartphone's built-in sensors. In addition map information, such as free and occupied space, is used.

The solution’s complexity is very low; besides, the smartphones and beacons no additional hardware or infrastructure is required. This reduces the initial and ongoing costs. The whole localization takes place on the users' smartphones. Compared to other approaches, the location estimation is very robust. During the evaluation, a user’s stationary location, with a mean error of 2.29m was achieved. Furthermore, a user’s path in the test environment could be tracked. In addition, the solution's algorithm detects wrong position estimations to recover.}

\newcommand{\ausgabedatum}{01.11.2014}
\newcommand{\abgabedatum}{01.01.1900}
\newcommand{\autor}{Thomas Bopst}
\newcommand{\autorStrasse}{Albert-Gebhardt-Str. 5}
\newcommand{\autorPLZ}{79761}
\newcommand{\autorOrt}{ Waldshut-Tiengen}
\newcommand{\autorGeburtsort}{München}
\newcommand{\autorGeburtsdatum}{31.01.1990 }
\newcommand{\prueferA}{Prof. Dr. Oliver Bittel}
\newcommand{\prueferB}{M. Sc. Michael Blaich}
\newcommand{\firma}{HTWG-Konstanz}
\newcommand{\studiengang}{Master of Science Informatik}


\begin{document}

% select language
\selectlanguage{german}

 % set pagecount style to i,ii,...
\setcounter{page}{1}
\pagenumbering{roman}


% HTWG-Template
% -------------
\include{template/cover}
\include{template/title}
\include{template/abstract}
\include{template/affidavit}

% change language to english
\selectlanguage{english}

% Abbreviations
\include{chapters/00_abbreviation}
\newpage

% Table of contents
\tableofcontents
\newpage
%\listoffigures
%\listoftables

% Content
% -------
\setcounter{page}{1} % set pagecount style to 1, 2, ...
\pagenumbering{arabic}

\include{chapters/10_introduction}
\include{chapters/05_fundamentals}
\include{chapters/20_ibeacons}
\include{chapters/30_sensors}
\include{chapters/40_algorithm}
\include{chapters/50_evaluation}
\include{chapters/60_conclusion}

%\appendix
%\include{chapters/90_appendix}

\addcontentsline{toc}{chapter}{References}
%\bibliographystyle{IEEEtranS}
\bibliographystyle{apa}
%\nocite{*}
\bibliography{chapters/99_references}

\end{document}
